\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\resumeItem}[1]{\item\small{{#1 \vspace{-2pt}}}}
\newcommand{\resumeSubheading}[4]{\vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}}
\newcommand{\resumeProjectHeading}[2]{\item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]} 
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}

\begin{document}

\begin{center}
    {\Huge \scshape Hetkumar Patel } \\ \vspace{1pt}
    Toronto, ON \\ \vspace{1pt}
    \small \faPhone\ (647) 835-3408  ~ \href{mailto:hetkumar.patel1403@gmail.com}{\faEnvelope~hetkumarl1403@gmail.com} ~ 
    \href{https://linkedin.com/in/h3t08}{\faLinkedin\ LinkedIn} ~
    \href{https://github.com/het0814}{\faGithub\ Github} ~
    \href{https://het0814.github.io/}{\faGlobe~Portfolio Website}
\end{center}

\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Sheridan College}{Jan. 2022 -- Apr. 2025}
      {Honours Bachelor of Computer Science (Data Analytics) | GPA: 3.7 (Honors)}{Ontario, Canada}
  \resumeSubHeadingListEnd

\section{Technical Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Artificial Intelligence Researcher (Part-Time)}{Sep. 2024 -- Apr. 2025}
      {Sheridan College, Centre for Applied AI}{Oakville, ON}
      \resumeItemListStart
        \resumeItem{Designed AI/ML pipelines for fleet management optimization, improving operational visibility and reducing manual effort by 40\%.}
        \resumeItem{Developed an LLM-based KPI scorecard system, enabling automated performance tracking from industry documents and cutting analysis time by 60\%.}
        \resumeItem{Applied BERTopic to uncover key trends from fleet reports, leading to a 35\% improvement in strategic insight delivery for stakeholders.}
        \resumeItem{Presented findings bi-weekly to cross-functional partners, aligning research outcomes with business objectives and accelerating deployment decisions.}
      \resumeItemListEnd

    \resumeSubheading
      {AI/ML Software Developer (CO-OP)}{May 2024 -- Sep. 2024}
      {NARYANT, Centre for Applied AI}{Oakville, ON}
      \resumeItemListStart
        \resumeItem{Built CTGAN-based synthetic mobility data pipeline for SUMO simulations.}
        \resumeItem{Achieved 92\% accuracy in transportation mode detection model.}
        \resumeItem{Implemented scalable ML models using Python, Pandas, Scikit-learn, TensorFlow.}
      \resumeItemListEnd

    \resumeSubheading
      {IIoT Developer (CO-OP)}{May 2023 -- Feb. 2024}
      {Magna International}{Milton, ON}
      \resumeItemListStart
        \resumeItem{Developed Ignition web pages to monitor machinery and detect faults.}
        \resumeItem{Modified PLC code and used Python for live data visualization.}
        \resumeItem{Reduced troubleshooting time by 85\% and improved monitoring accuracy by 97\%.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd
  
\section{Projects}
  \resumeSubHeadingListStart
    \resumeProjectHeading
      {\textbf{ContextIQ: RAG-based Chatbot} $|$ \emph{FastAPI, React, Python, Chroma}}{Mar. 2025}
      \resumeItemListStart
        \resumeItem{Built a full-stack RAG chatbot to provide context-aware responses using document/URL ingestion.}
      \resumeItemListEnd
    \resumeProjectHeading
      {\textbf{Climate Change Prediction} $|$ \emph{Time Series, ARIMA, Python}}{Mar. 2025}
      \resumeItemListStart
        \resumeItem{Forecasted climate trends using historical datasets and ARIMA models.}
      \resumeItemListEnd
    \resumeProjectHeading
      {\textbf{Synthetic Mobility Data Generator} $|$ \emph{CTGAN, Python}}{May 2024}
      \resumeItemListStart
        \resumeItem{Created synthetic data generator for SUMO mobility simulations.}
      \resumeItemListEnd
    \resumeProjectHeading
      {\textbf{SnapCal} $|$ \emph{Flask, Inception v2, Python}}{Mar. 2024}
      \resumeItemListStart
        \resumeItem{Deployed food image recognition app with calorie estimation using deep learning.}
      \resumeItemListEnd
    \resumeProjectHeading
      {\textbf{Inventory Management System} $|$ \emph{C\#, ASP.NET}}{Dec. 2023}
      \resumeItemListStart
        \resumeItem{Built inventory and supplier management system with forecasting features.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
  \small{\item{
   \textbf{Programming Languages:} Python, R, JavaScript, C, C++, C\# \\
   \textbf{Web Dev:} HTML, CSS, JavaScript, ASP.NET, Flask, Spring Boot \\
   \textbf{Big Data:} Hadoop, Spark, MongoDB, MySQL, SQLite \\
   \textbf{Visualizations and Cloud Tools:} Power BI, Tableau, Git, Docker, CI/CD, Ignition, AWS, GCP \\
   \textbf{AI/ML:} LLMs, BERTopic, TensorFlow, PyTorch, NLP, Scikit-learn, Hugging Face, LangChain, OpenCV, MLFlow.
  }}
 \end{itemize}

\section{Leadership / Extracurricular}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Volunteer Student Mentor}{2023 -- 2024}
      {Sheridan College Peer Mentorship Program}{Ontario, Canada}
  \resumeSubHeadingListEnd

\end{document}
  
